Data_visualization

### 2018-08-30 Rmd/Data_visualization.Rmd
rmd with ratio ggplot

>>>>

```{r, fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae")
```

```{r, fig.width=8}
pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae")
```

```{r, fig.width=8}
pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae")
```
